Interval Probability for Fuzzy Quantum Theories

### 2016-05-08 prob.tex
Add citation... However, Lazzarini's seems Italian...
prob.tex \subsection{Buffon's Needle Problem} Add comments...

In an actual experiment with 500 needles, it was found that 321
crossed a line which gives a probability of $0.642$. In a larger
experiment with $3408$ needles, the probability was calculated to be
$0.6366197193098592$.\\
\yutsung{
May I confirm how many times needle cross the line within $3408$ needles?
Because $\frac{2169}{3408}$ is almost $0.6364436619718310$, and
$\frac{2170}{3408}$ is almost $0.6367370892018779$, both of them are not
close to $0.6366197193098592$ enough\ldots }\\
\amr{
There are several articles and papers on the experiment. I got these
values from wikipedia and mathworld. We need to get precise references
and cite the papers describing the experiments. The actual values
don't matter though.
}
Comparing the values to the idealized mathematical value, we see that
the observed probability approaches $\frac{2}{\pi}$ but only if
\emph{larger and larger resources} are expended.

>>>>

In an actual experiment with 500 needles, it was found that 321
crossed a line which gives a probability of $0.642$. In a larger
experiment with $3408$ needles, the probability was calculated to be
$0.6366197193098592$~\cite{Lazzarini1901,Uspenskyothers1937}.\\
\yutsung{
May I confirm how many times needle cross the line within $3408$ needles?
Because $\frac{2169}{3408}$ is almost $0.6364436619718310$, and
$\frac{2170}{3408}$ is almost $0.6367370892018779$, both of them are not
close to $0.6366197193098592$ enough\ldots 
}\\
\amr{
There are several articles and papers on the experiment. I got these
values from wikipedia and mathworld. We need to get precise references
and cite the papers describing the experiments. The actual values
don't matter though.
}\\
\yutsung{
Although I don't know Italian, it seems that Lazzarini~\cite{Lazzarini1901}
used the needle with length 2.5, and the length among lines is 3.
When he tossed needles 3408 times, he got 1808 crossing, and 
\[
\pi\approx\frac{2\cdot2.5\cdot3408}{3\cdot1808}=\frac{355}{113}\approx3.1415929
\]
However, his paper was be criticized in Wikipedia, because $\frac{355}{113}$
is the best rational approximation of $\pi$ for small intergers.
How can his experiment just gave this number?

Uspensky~\cite{Uspenskyothers1937} and Buffon~\cite{Buffon1777}
are books. I will check out \cite{Uspenskyothers1937} on Sunday,
and \cite{Buffon1777} on Monday...
}\\
Comparing the values to the idealized mathematical value, we see that
the observed probability approaches $\frac{2}{\pi}$ but only if
\emph{larger and larger resources} are expended.
